How do agents form inflation expectations? evidences from cross-moment estimation and the uncertainty

### 2020-08-20 paper/InfVar.tex
moved out the literature folder.

	Different from the previous two theories, diagnostic expectation (\cite{bordalo2018diagnostic}) is developed in the literature to account for extrapolative expectations that feature overreactions to the news. Both SE and NI deviate from FIRE in terms of the information set available to the agents, while DE deviates from FIRE in terms of the processing of an otherwise fully updated information set.

@@

 while since agents extrapolates whatever is considered 
		\begin{eqnarray}
		\begin{aligned}
			\bar y_{i,t+h|t}  =  \rho^h y_{t} + \theta_i (\rho^h y_t - \bar y_{i,t+h|t-1})
		\end{aligned}
	\end{eqnarray}

	 I allow $\theta$ to be different across different agents, therefore, I add the subscript $i$ to the parameter. Since agents are equally informed about the realizations of the variable, the only room for disagreement to rise is either difference in the initial information set or the degree of overreaction differs across people. To capture this, I assume $\theta_i$ to follow a normal distribution across the population with a variance of $\sigma_{\epsilon}$. It will be estimated along with $\theta$.

@@

Table \ref{SMM_Est_SPF} presents the SMM estimates of different model parameters. For each theory, I estimate the theory both in two-steps or jointly using expectation and inflation data. Different rows without each panel reports the estimates by using different sets of moments:forecast errors only,  forecast error and disagreement, and the two plus uncertainty.

@@

\subsection{The scoring card of different theories (draft in process)}}

Table \ref{scoringcard} presents the evaluation of the three theories based on its sensitivity of goodnedss of fit and parameter estimate with respect to four criteria. Based on the evaluation, sticky expectation seems to capture the average behavior of expectations better than the other two theories. Diagnostic expectation shows similar degree of performance according to these criteria, but the average estimation does not show overreaction in lign with the premise of the theory.

	\begin{table}[p]
	\caption{A scoring card of different theory} 
	\label{scoringcard}
	\centering
	\begin{tabular}{llll}
		\hline 
		Criteria                                    & SE     & NI  & DE     \\
		\hline 
		Sensitive to moments used for estimation?   & No     & No  & No     \\
		Sensitive to the assumed inflation process? & No     & Yes & No     \\
		Sensitive to a two-step or joint estimate?  & No     & Yes & No     \\
		Sensitive to the type of agents?            & Yes    & Yes & Yes    \\
		Matching with FE                            & Yes    & Yes & Yes    \\
		Matching with disagreement                  & Yes    & No  & Unsure \\
		Matching with uncertainty                   & Unsure & No  & No    \\
		\hline 
	\end{tabular}
\end{table}

>>>>

	Different from the previous two theories, diagnostic expectation (\cite{bordalo2018diagnostic}) is developed in the literature to account for extrapolative expectations that feature overreactions to the news  (\cite{bordalo2018over}). Both SE and NI deviate from FIRE in terms of the information set available to the agents, while DE deviates from FIRE in terms of the processing of an otherwise fully updated information set.

@@

		\begin{eqnarray}
		\begin{aligned}
			\bar y_{i,t+h|t}  =  \rho^h y_{t} + \theta_i (\rho^h y_t - \bar y_{i,t+h|t-1})
		\end{aligned}
	\end{eqnarray}

	 I allow $\theta$ to be different across different agents, therefore, I add the subscript $i$ to the parameter. Since agents are equally informed about the realizations of the variable, the only room for disagreement to rise is either difference in the initial information set or the degree of overreaction differs across people. To capture this, I assume $\theta_i$ to follow a normal distribution across the population with a variance of $\sigma_{\epsilon}$. It will be estimated along with $\theta_i$.

@@

Table \ref{SMM_Est_SPF} presents the SMM estimates of different model parameters. For each theory, I estimate the theory both in two steps or jointly using expectations and inflation data. Different rows within each panel reports the estimates depending on various choices of moments used for estimation: forecast errors only,  forecast error and disagreement, and the two plus uncertainty.

@@

\subsection{The scoring card of different theories (draft in process)}

Table \ref{scoringcard} reports my evaluation of the three theories based on four sensitivity criteria we discussed in the previous section. According to this evaluation, the sticky expectation seems to capture the average behavior of expectations better than the other two theories. Diagnostic expectation shows similar degree of performance according to these criteria, but the average estimation does not show overreaction in lign with the premise of the theory.

	\begin{table}[p]
	\caption{A scoring card of different theories} 
	\label{scoringcard}
	\centering
	\begin{tabular}{llll}
		\hline 
		Criteria                                    & SE     & NI  & DE     \\
		\hline 
		Sensitive to moments used for estimation?   & No     & No  & No     \\
		Sensitive to the assumed inflation process? & No     & Yes & No     \\
		Sensitive to a two-step or joint estimate?  & No     & Yes & No     \\
		Sensitive to the type of agents?            & Yes    & Yes & Yes    \\
		Matching with FE                            & Yes    & Yes & Yes    \\
		Matching with disagreement                  & Yes    & No  & Unsure \\
		Matching with uncertainty                   & Unsure & No  & No    \\
		\hline 
	\end{tabular}
\end{table}
